---
title: "Homework Assignment 3"
author: "Johnson ODEJIDE"
date: "2023-02-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## 1

Two methods of R coding to extract the first element and the last element.

```{r}
Vector1 <- (c( 10, 19, 121, 83, 63, 7, 77, 61, 51, 97, 123, 41))

Vector1[c(1, 12)]
Vector1[-c(2:11)]
```

## 2

Two methods of R coding to extract all of the elements that are less than 60.

```{r}
Vector1[Vector1 < 60]
Vector1[!Vector1 >= 60]
```

## 3

Two methods of R coding to extract all numbers that are not divisible by 2 or 3.

```{r}
Vector1[!Vector1 %% 2 == 0 & !Vector1 %% 3 == 0]
Vector1[Vector1 %% 2 != 0 & Vector1 %% 3 != 0]
```


## 4

Two R coding methods to confirm that `Vector1` does not have missing values

```{r}
Vector1[is.na(Vector1)]
is.na(Vector1)
```


## 5

R coding to confirm that "`pear`" is a character element in the list.

```{r}
myList <-  list(TRUE, 12.35, "pear", 48, c = 3:8, list(23, "team"))
myList 

is.character(myList[[3]])
```


## 6

R coding to extract the first three elements of the list.

```{r}
myList[1:3]
```

## 7 

Use the **$** _operator_ to extract the element “`pear`” from your list.

```{r}
# Recreate the list to assign a variable to "pear"
myListNew <-  list(TRUE, 12.35, p = "pear", 48, c = 3:8, list(23, "team"))
myListNew$p
```


## 8

R code to write a function to solve the following quadratic equations by using the quadratic formula.

`a)  x^2 - 3x - 28 = 0`

`b)  x^2 + x  - 30 = 0`

`c) 3x^2 + 14x + 8 = 0`

`d) 2x^2 + 11x = 6`


```{r}

solve_quadratic <- function(a, b, c){
  x1 = (-b + sqrt(b^2 - (4*a*c))) / (2*a)
  x2 = (-b - sqrt(b^2 - (4*a*c))) / (2*a)
  
  print(paste("The solution of the quadratic equation when a = ", a, ", b = ", b, ", and c = ", c, " are ", round(x1, digits = 2), " and ", round(x2, digits = 2)))
}

### Solution for x^2 - 3x - 28 = 0
solve_quadratic(1, -3, -28)

### Solution for x^2 + x  - 30 = 0                                      
solve_quadratic(1, 1, -30)

### Solution for 3x^2+ 14x + 8 = 0
solve_quadratic(3, 14, 8)

### Solution 2x^2 + 11x = 6
solve_quadratic(2, 11, -6)
```

## 9

R code that will produce the Tibble (an Augmented Vector).
**Do not simply type or copy and paste. You must show and use R coding that will output the tibble.**

```{r}
tib_augvector <- tibble::tibble(x = 1:10, y = 10:1, z = seq(from = 5, to = 0.5, by = -0.5))
tib_augvector
```


## 10

map function coding to find the Interquartile Range for each column of the tibble from number 9

```{r}
round(map_dbl(tib_augvector, IQR), digits = 2)
```

