---
title: "Homework 4"
author: "Johnson ODEJIDE"
date: "2023-02-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## 1

Use the R function nrow to confirm that the iris data frame has 150 rows. Then use and show R code that features a map function to confirm that the iris data frame has 150 rows.

```{r}
nrow(iris)

map(iris, length)
```

## 2

Use and show R code that features a nested loop that will produce the  5 by 3 matrix shown below

```{r}
my_matrix <- matrix(nrow = 3, ncol = 5)

for(i in nrow(my_matrix):1){
  for(j in ncol(my_matrix):1){
    my_matrix[i, j] = (2 * j)-(i + j)
  }
}
  
my_matrix

```

## 3

Use and show R code that will produce a tibble that features 10 randomly generated values that are normally distributed, with means of -10, 0, 10 and 100 respectfully.  Run your code again, producing a second tibble, that confirms random values, hence the second table will not have the same values.

```{r}
rand_num1 <- tibble(
  a = rnorm(10, -10),
  b = rnorm(10, 0),
  c = rnorm(10, 10),
  d = rnorm(10, 100)
)
rand_num1

rand_num2 <- tibble(
  a = rnorm(10, -10),
  b = rnorm(10, 0),
  c = rnorm(10, 10),
  d = rnorm(10, 100)
)
rand_num2

```
**The two tables have different random values**

## 4

` X <- list(12, 14, 15, 18, 19, 22,10,18,18) `

` Mean <- list(16, 16, 16, 16, 16,16,16,16,16) `

` sd <- list(2, 2, 2, 2, 2,2,2,2,2) `

### b

In statistics, a z score indicates the standard deviation distance between the mean and a specific value of the data set. What formula is used to find a z score? Use and show R coding that features a map function to iteratively find z scores across the lists given above.

**The formula for z score is (X - Mean) / sd**

```{r}
X <- list(12, 14, 15, 18, 19, 22,10,18,18)
Mean <- list(16, 16, 16, 16, 16,16,16,16,16)
sd <- list(2, 2, 2, 2, 2,2,2,2,2)

# zscore = (x - Mean) / sd

output2 <- vector("double") 
for (i in seq_along(X)) {
  output2[[i]] <- (X[[i]] - Mean[[i]]) / sd[[i]]
}
output2

```


### c

The test statistic for a population mean is given by the formula `((X - mean)/(s/sqrt(n))` Use and show R coding that features a map function to iteratively find test statistics for population means across the lists given above.

```{r}
output2 <- vector("double")
for (i in seq_along(X)) {
  output2[[i]] <- (X[[i]] - Mean[[i]]) / (sd[[i]] / sqrt(i))
}
output2
```

## 5

`V = c(10,15,17,22,32,38,42)`

### a

Another purr package function is the keep( ) function. Research, explore, and use the keep( ) function to extract all number from the vector V given above that are less than 20


```{r}
V = c(10,15,17,22,32,38,42)

V %>% 
  keep(.<20)

```


### b

Another purr package function is the discard( ) function. Research, explore, and use the discard( ) function to eliminate all numbers from the vector V given above that are less than 20

```{r}
V %>% 
  discard(.<20)
```


## 6

Another purr package function is the **safely( )** function. Research, explore, and apply the 
 safely( ) function  to the given vector below as illustrated.
  `U = list(10,15,"mary",22,32,"james",42)`
  
  `map(U, safely(~ .x + 15))`
  
In four or five sentences, explain the specific output for this problem and how the definition and the application of the safely( ) function is used.

```{r}
U = list(10,15,"mary",22,32,"james",42)
map(U, safely(~ .x + 15))
```
**Safely()** is a function used with map that allows an execution of a program without having to terminate. It rather returns a list of two element. An element `$result` showing the actual value of the result as well an element `$error` with the value of **NULL** is returned if the operation is successful. However, if the operation fails, `$result` is returned as **NULL** and the `$error` displays the actual error encountered during the course of the operation.
