---
title: "Lab1"
author: "Johnson ODEJIDE"
date: "2023-01-18"
output: 
  word_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE}
library(lubridate)
library(tidyverse)
```

## Question 1

Use and show R code to extract the month from the following datetime designation;

`datetime2 <- ymd_hms("2021-11-13 10:05:31")`
`datetime2`

```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

month(datetime2)
```

## Question 2

Use and show R code to extract the day of the week from the following datetime designation;
`datetime2 <- ymd_hms("2021-11-13 10:05:31")`
`datetime2`

```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

wday(datetime2)
```

## Question 3

Use and show R code to change the month to 8, and the hour to 5 for the following datetime designation
`datetime2 <- ymd_hms("2021-11-13 10:05:31")`
`datetime2`

```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

update(datetime2, month = 8, hour = 5)
datetime2
```

## Question 4

Use and show R code to change 6 hours to seconds. 

```{r}
dhours(6)
```

## Question 5

Use and show R code to change 4 days to seconds.

```{r}
ddays(4)
```

## Question 6

Use and show R code to add 7 years to 30 days.

```{r}
dyears(7) + ddays(30)
```

## Question 7

Use and show R code to determine how many weeks there are from today's date to a year from now.

```{r}
next_year <- today() + years(1)

(today() %--% next_year)/weeks(1)
```

## Question 8

Use and show R code to determine how many days there are between today's date and June 28, 2022.

```{r}
jun_28_day <- ymd("2022-06-28")

(today() %--% jun_28_day)/days(1)
```