---
title: "Lab 4"
author: "Johnson ODEJIDE"
date: "2023-02-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## 1

R code (a map function) that iteratively to find the square of the sums across the vectors.

```{r}
x <- list(2, 4, 5, 9, 1)
y <- list(8, 7, 2, 8, 3)
z <- list(1, 8, 5, 4, 2)

pmap_dbl(list(x,y,z), function(first, second, third) (first + second + third)^2)
```

## 2

R code that will output a statement that is descriptive for all rows of the data table. The first row is given below.  Your code should produce the other specific statements. `John who is Male, has a salary that is 65000 dollars per year.`

```{r}
tribble( ~Student,  ~Gender,    ~Salary,
         "John",   "Male",       65000,
         "Alice",  "Female",    73000,
         "Juan",   "Male",       66000,
         "Beth",  "Female",    71500,
         "Denise", "Female",  82000
) -> table

table

table %>% 
  pmap_chr(~ str_glue("{..1} is {..2}, has a salary that is {..3} dollars per year."))
```

## 3

A 5 by 5 matrix that whose matrix elements are sums of the corresponding columns and rows.

```{r}
myMatrix <- matrix(nrow = 5, ncol = 5)

for(i in 1:nrow(myMatrix)){
  for(j in 1:ncol(myMatrix)){
    myMatrix[i, j] = i + j
  }
}
myMatrix
```


## 4

Loop coding to produce the number sequence
**Note that the numbers 5 and 10 are missing**

```{r}
for(i in 1:20){
  if(i == 5 | i == 10){
    next
  }
  print(i)
}
```

