---
title: "Lab 3"
author: "Johnson ODEJIDE"
date: "2023-02-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## 1

`V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")` is atomic because the vector contains only one type of data, that is, a character string. Atomic vectors are the ones that use the combine function.


## 2
```{r}
V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals")
V[3]
```


## 3
```{r}
V[c(1, 3, 5)]
```


## 4
```{r}
V[-1]

V[c(2:5)]
```


## 5

The vector is a list because it consists of different types of objects It consists of a character string but it also consist of a list, as well as integer.

The vector consist of ***an atomic vector***, ***character string***, ***double***, ***list***


## 6
```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
length(K)
```



## 7
```{r}
K[4]
```



## 8
```{r}
K[]
```

## 9a
```{r}
tribble( ~x,    ~y,    ~w,    ~z,
         210,   300,   220,   180,
         102,   100,   119,   187,
         176,   175,   188,   173,
         87,    95,   91,     94,
         202,   210,  234,    218,
         110,   122,  131,    128,
) -> dt
dt

map_dbl(dt, mean)
```


## 9b
```{r}
map_dbl(dt, sd)
```


## 9c
```{r}
# dt %>% 
#   sqrt(.)
dt %>% 
  map(sqrt)
```


## 9d
```{r}
dt %>% 
  summary()
```