---
title: "Classwork Lab on Data Tables"
author: "Johnson ODEJIDE"
date: "2023-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(tidyverse)
library(dplyr)
library(data.table)

flights <- fread("nycdata.csv")

head(flights)
```

**1)** Use and show data.table code to select the variables year, month, day, and hour from the imported flights data

```{r}
flights[, .(year, month, day, hour)]
```

**2)** Use and show data. table code to produce a table that shows a carrier of DL, an origin of JFK and a destination of SEA

```{r}
flights[carrier == "DL" & origin == "JFK" & dest == "SEA"]
```

**3)** Use and show data.table code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
flights[carrier == "UA" & month == 3 & air_time < 330]
```


**4)** Use and show tidyverse code to produce a table that shows a carrier of UA, a month of March, and an airtime that is below 330.

```{r}
flights %>% 
  filter(carrier == "UA", month == 3, air_time < 330)
```

**5)** Use the data.table method to add a variable called speed that is the average air speed of the plane in miles per hour. 

```{r}
flights[, c("speed") := .(distance / hour)]
flights
```

**6)** Use the tidyverse method to add a variable called speed that is the average air speed of the plane in miles per hour.

```{r}
flights %>% 
  mutate(speed = (distance / hour))
```

**7)**
Show and use coding to change the carrier abbreviation of UA to UniitedAir,


**7a)** data.table method

```{r}
flights[carrier == "UA", carrier := "UniitedAir"]
flights
```

**7b)** tidyverse method  (Use a sequence of dplyr commands so that you can see the change in your table)

```{r}
flights %>%
  mutate(carrier = recode(carrier, "UA" = "UniitedAir")) ->
  flights
flights
```













